\documentclass[answers,a4paper,11pt]{exam}
\usepackage{hyperref}
\ifx\pdftexversion\undefined
\usepackage{epsfig}
\else
\usepackage[pdftex]{graphics}
\fi
\usepackage{epsfig}

\begin{document}
\extraheadheight{.5in}
\firstpageheader{\large\sf FMC1203}%
{\large\sf National University of Singapore\\ School of Computing \\
\LARGE\sf Reduction}%
{\large\sf Semester 2 11/12}
\firstpageheadrule
\pagestyle{headandfoot}

\begin{questions}
\question
A problem $P$ can be \textit{reduced} to another problem $Q$, if we can use a solution that solves $Q$ to help solves $P$.  The cost of solving $P$ is then $k$ times the cost of solving $Q$ plus the cost of reducing $P$ to $Q$, where $k$ is the number of times the solution of $Q$ is used.

Reducing one problem to another is useful in a few ways:
\begin{itemize}
		\item if we know how to solve $Q$, we can solve $P$
		\item if we know that $P$ is hard to solve, then $Q$ is also hard to solve
\end{itemize}

\newpage
\question
Show that the following problem can be reduced to the problem of sorting.
\begin{parts}
		\part Given an array of integers, find the median of the array
\fillwithdottedlines{2in}
		\part Given an array of integers and a integer $K$, find all pairs of numbers that sum up to $K$.
\fillwithdottedlines{2in}
		\part Given an array of integers, find if the elements in the array is unique.
\fillwithdottedlines{2in}
\end{parts}

\newpage
\question
Consider the following two problems: 

\textbf{3-COLLINEAR}: Given a set of points $P$,  are there three points in $P$ that lie on the same line?

\textbf{3-SUM}: Given a set of numbers $S$  are there three numbers in $S$ sum up to 0?

Show that 3-SUM can be reduced to 3-COLLINEAR.

%See \url{http://www.ssynth.co.uk/~gay/anagott.html}
\fillwithdottedlines{5in}

%\newpage
%\question
%Consider the \textbf{Traveling Salesmen Problem}: a saleman needs to visit $N$ cities, starting and ending at the same city.  The saleman wants to find the order to visit the $N$ cities such that the travel cost is less than
%
%\fillwithdottedlines{5in}

\newpage
\question
Consider the \textbf{Halting Problem}: Given a program $P$ and an input $I$, which $P$ halts when run with input $I$?  The halting problem can be shown to be \textit{undecidable} -- noone can write a program that decides if another program $P$ halts on a given input $I$.

Show that it is not possible to write a program that decides, given two programs $P_1$ and $P_2$, whether $P_1$ and $P_2$ will always give the same output given the same input.

\fillwithdottedlines{5in}

\newpage
\question
An optimization problem is one that has the form: find the maximum or minimum of of an objective function.  For example, the minimum spanning tree problem is an optimization problem: find the minimum cost of a spanning tree in a graph.

Each optimization problem has an equivalent \textit{decision version} of the problem: is there a solution such that the objective function is less than or greater than a given value $K$?  For example, is there a spanning tree in a graph with a cost less than $K$?

\fillwithdottedlines{5in}


\end{questions}
\end{document}
