\documentclass[answers,a4paper,11pt]{exam}
\usepackage{hyperref}
\ifx\pdftexversion\undefined
\usepackage{epsfig}
\else
\usepackage[pdftex]{graphics}
\fi
\usepackage{epsfig}

\begin{document}
\extraheadheight{.5in}
\firstpageheader{\large\sf FMC1203}%
{\large\sf National University of Singapore\\ School of Computing \\
\LARGE\sf Hashing}%
{\large\sf Semester 2 11/12}
\firstpageheadrule
\pagestyle{headandfoot}
A hash function is a mathematical function that maps one sequence of bits, called \textit{hash key} to another (usually shorter) sequence of bits, called \textit{hash value}.  Hash functions, with different properties, can be useful in many ways in computing.

\begin{questions}
\question
A hash function can have the following property: two keys that are similar are hashed into two very different values.

\begin{parts}
\part
Describe how such hash function can be useful in looking up a specific information from a large amount of data.
\fillwithdottedlines{3in}
\part
What is Bloom filter?  Describe how such hash function can be useful in Bloom filter.
\fillwithdottedlines{3in}
\end{parts}
\newpage
\question
A hash function can have the following property: two keys that are similar are hashed into similar values.

Explain how such hash function can be useful in detecting copyright infringement for video and audio files.
\fillwithdottedlines{3in}
\question
A hash function can have the following property: given a hashed value, it is difficult to find out which key is hashed to this value.  It is also difficult to find another key that is hashed to the same value.

Such hash function is especially useful in computer security.
\begin{parts}
\part
Explain how such hash function is useful for storing passwords.
\fillwithdottedlines{2in}
\part
Explain how such hash function can be used to prevent cheating in two player games.
\fillwithdottedlines{2in}
\part
Explain how such hash function can be used to verify the correctness of a file or a message.
\fillwithdottedlines{2in}
\part
Explain how such hash function can be used to verify the authenticity of a file or a message.
\fillwithdottedlines{2in}
\end{parts}

\end{questions}
\end{document}
