
\documentclass[answers,a4paper,11pt]{exam}
\usepackage{hyperref}
\ifx\pdftexversion\undefined
\usepackage{epsfig}
\else
\usepackage[pdftex]{graphics}
\fi
\usepackage{epsfig}

\begin{document}
\extraheadheight{.5in}
\firstpageheader{\large\sf FMC1203}%
{\large\sf National University of Singapore\\ School of Computing \\
\LARGE\sf Project}%
{\large\sf Semester 2 11/12}
\firstpageheadrule
\pagestyle{headandfoot}

You wake up one morning in a strange and unfamiliar place.  You found out that you have been magically transport through time and space to the Kingdom of Twef-o-Thri!  

The King of Twef-o-Thri has summoned you apparently to help him with some of his projects.  He has heard that, in your world, SMS services, social networking sites such as Facebook, and search engines such as Google, have transformed the life of your people, and would like to replicate the success in his kingdom.  

The King will return you to your world only if you help him with one of his projects.  You thought, ``I am a computing student, I can do this!'' So you ask for a computer and Internet connection so that you can get to work.  Alas!  You found out that in the Kingdom of Twef-o-Thri, there is no electricity and computers do not exists!  The level of technology is equivalent to 15th century in your world.

The King then explains what he wants to do, more specifically.  He wants to:

\begin{itemize}
\item
build a mobile messaging system (similar to SMS), where anyone can send a message to anyone within the Kingdom.  He imagines that anyone can scribble a short message on a piece of paper, write the identity of the recipient on the paper, deposit it in a “messaging box” (available everywhere on the streets of Twef-o-Thri), and the paper will be delivered to the recipient no matter where the recipient is.
\item
build a social news feed system (similar to Facebook), where there is a pin-up board at every home, which will be updated periodically with the latest happenings of the friends of the family.  Anyone can write a status update on a piece of paper, deposit it in a “status update box” (also available everywhere on the streets of Twef-o-Thri) and have it updated on the pin-up board at each of his or her friends’ home.  
\item
build an information search system (similar to Google), where anyone can write a query, deposit it in a “search query box” (also available everywhere on the streets of Twef-o-Thri), and have a stack of papers containing information from published books and daily news that is related to the query delivered to his or her home. 
\end{itemize}

The King is willing to commit some amount of money and manpower to get these three systems working in his kingdom.  You can request for manpower to do work, such as writing, delivering, sorting, and storing papers.  You can request for new buildings for various purposes, such as storage warehouses and office buildings.  The King, however, wants you to design the system so that it is as efficient and scalable as possible.

The King gives you until \textbf{12 April 2012 (according your world’s clock) to submit a detailed 6-page report (10 point fonts, single spacing, A4-size) and give a 30-minute presentation} on how you would build one of the above system in the Kingdom of Twef-o-Thri.   

You are worried at first: ``how am I going to pull this off in a world without computers?''  Then you remember you lessons in FMC1203, where you learnt about various computational thinking methods that could be applied to many non-computing situations, such as abstraction, decomposition, composition, indirection, caching, hashing, distribution, pipelining.  So you decided to \textbf{incorporate as many of these thinking methods as possible} into the design of the system.  You also decided to \textbf{highlight which part of your design makes use of which concept} from FMC1203 in your report and presentation, so that the King of Twef-o-Thri can learn about computational thinking from you. 
\end{document}
